paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

### Conclusions and Relevance
Our analysis confirms the results of Brown et al. showing a negative association between restrictive abortion legislation and abortion rates based on both the 18 states they analyized and based on data from all 50 states.  We furthered the analysis to additional outcomes and found positive associations between restrictions and infant death rates.

>>>>

### Conclusions and Relevance
Our analysis confirms the results of Brown et al. showing a negative association between restrictive abortion legislation and abortion rates based on both the 18 states they analyized and based on data from all 50 states.  We furthered the analysis to additional outcomes and found positive associations between restrictions and infant death rates, and showed that restrictions do not have a significant association with birth rates.
